Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2025-03-14 manuscript.qmd
Changing fonts in fugures

theme_replace(
    axis.text = element_text(size = axis_text_size), 
    axis.title.x = element_text(size = axis_title_size, angle = 0, margin = ggplot2::margin (t = 10)), 
    axis.title.y = element_text(size = axis_title_size, angle = 90, margin = ggplot2::margin (r = 10)), 
    plot.title = element_text(size = title_size, hjust = 0.5, face = "bold"), 
    legend.text = element_text(size = axis_title_size), 
    legend.title = element_text(size = axis_title_size, face = "bold"), 
    strip.text = element_text(size = axis_title_size, face = "bold", color = "white"), 
    strip.background = element_rect(fill = "#000080"), 
    panel.background = element_rect(fill = "#f3faff"), panel.grid.major = element_line(colour = "white"), 
    panel.spacing = unit(2, "lines")
)

@@

    mutate (strategy = paste (app.mthd, incorp, sep = " - ")) %>%
    mutate (strategy = recode (strategy, "bc - none" = "A", "bc - shallow" = "B", "bc - deep" = "C", "bsth - none" = "D", "os - none" = "E", "ts - none" = "F")) %>%

@@

Figure_1
```

@@

@@

    mutate (method = recode (method, "alfam2" = "A", "lasso" = "B", "random forest" = "C", "xgboost" = "D")) %>%

@@

@@

@@

```{r, fig.width = 10, fig.height = 12}
df_importance_rf = randomForest::importance (random_forest_model) %>%
    as.data.frame %>%
    rownames_to_column (var = "Variable") %>%
    mutate (`%IncMSE` = `%IncMSE` / max (`%IncMSE`)) %>%
    mutate (type = "A")

@@

```{r, fig.width = 10, fig.height = 12}
df_importance_xgb = xgboost::xgb.importance (model = xgboost_model) %>%
    mutate (Gain = Gain / max (Gain)) %>%
    mutate (type = "B")

@@

@@

@@

plot_shap_rf_2 = plot_shap_rf +
    annotate (geom = "label", label = "A", size = 22, fontface = "bold", x = 45, y = 1.5, fill = "#000080", color = "white") +
    xlim (c (- 18, 45)) +
    theme (legend.position = "none", 
          plot.margin = unit (c (0, 0, 1, 0), "cm"),
          axis.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks.x = element_blank())

plot_shap_xgboost_2 = plot_shap_xgboost +
    annotate (geom = "label", label = "B", size = 22, fontface = "bold", x = 45, y = 1.5, fill = "#000080", color = "white") +
    xlim (c (- 18, 45)) + 
    theme (legend.position = "none", 
          plot.margin = unit (c (0, 0, 1, 0), "cm"),
          axis.title.x = element_text (margin = ggplot2::margin (t = 10, b = 20)))

tiff (file = "figures/Figure_5.tiff", width = 1000, height = 900)
do.call ("grid.arrange", 
         c (list(plot_shap_rf_2, 
                 plot_shap_xgboost_2, 
                 legend), 
            list(layout_matrix = as.matrix(c (1, 2, 3)),
                  heights = c (0.8, 1, 0.2))))
dev.off()
```

@@

@@

@@

@@

```{r, fig.height = 8, fig.width = 10}
Figure_9 = rbind (
    data %>% select (temp = Tem) %>% mutate (data = "Data from Peng Xu et al (2024)"),
    data_alfam2 %>% select (temp = air.temp) %>% mutate (data = "Data used for the alfam2 model")
) %>%

@@

```{r}
rbind (
    data %>% select (temp = Tem) %>% mutate (data = "Data from Peng Xu et al (2024)"),
    data_alfam2 %>% select (temp = air.temp) %>% mutate (data = "Data used for the alfam2 model")
) %>%

>>>>

theme_replace(
    axis.text = element_text(size = axis_text_size), 
    axis.title.x = element_text(size = axis_title_size, angle = 0, margin = ggplot2::margin (t = 10)), 
    axis.title.y = element_text(size = axis_title_size, angle = 90, margin = ggplot2::margin (r = 10)), 
    plot.title = element_text(size = title_size, hjust = 0.5, face = "bold"), 
    legend.text = element_text(size = axis_title_size), 
    legend.title = element_text(size = axis_title_size, face = "bold"), 
    strip.text = element_text(size = axis_title_size, face = "bold", color = "white"), 
    strip.background = element_rect(fill = "#000080"), 
    panel.background = element_rect(fill = "#f3faff"), panel.grid.major = element_line(colour = "white"), 
    panel.spacing = unit(2, "lines"),
    text = element_text (family = "Times")
)

@@

    mutate (strategy = paste (app.mthd, incorp, sep = " - ")) %>%
    #mutate (strategy = recode (strategy, "bc - none" = "A", "bc - shallow" = "B", "bc - deep" = "C", "bsth - none" = "D", "os - none" = "E", "ts - none" = "F")) %>%
    mutate (strategy = recode (strategy, "bc - none" = "Broadcast", "bc - shallow" = "Shallow incorporation", "bc - deep" = "Deep incorporation", "bsth - none" = "Trailing hoses", "ts - none" = "Trailing shoes", "os - none" = "Open slot")) %>%

    mutate (strategy = factor (strategy, levels = c ("Broadcast", "Shallow incorporation", "Deep incorporation", "Trailing hoses", "Trailing shoes", "Open slot"))) %>%

@@

Figure_1

png (file = "figures/Figure_1.png", width = 1000, height = 700)
Figure_1
dev.off()
```

@@

```{r, include = FALSE}
png (file = "figures/Figure_10.png", width = 1000, height = 1100)
plot_residuals_complete_dataset
dev.off()

png (file = "figures/Figure_11.png", width = 1000, height = 1100)
plot_residuals_evaluation_subset
dev.off()
```

@@

    mutate (method = recode (method, "alfam2" = "ALFAM2", "lasso" = "Lasso", "random forest" = "Random forest", "xgboost" = "Gradient boosting")) %>%

    mutate (method = factor (method, levels = c ("ALFAM2", "Lasso", "Random forest", "Gradient boosting"))) %>%

@@

```{r, include = FALSE}
png (file = "figures/Figure_2.png", width = 1000, height = 700)
Figure_2
dev.off()
```

@@

    select (- MSE, - RMSE, - MAE, - MBE) %>%

    pivot_longer (cols = c (Pearsons_r, ME)) %>%

    mutate (variation = (abs(value) / abs(value [method == "alfam2"]) - 1) * 100, .by = c(name, dataset)) %>%
    mutate (variation = round (variation, digits = 1)) %>%
    mutate (value = round (value, digits = 2)) %>%

@@

```{r, fig.width = 10, fig.height = 12}
df_importance_rf = randomForest::importance (random_forest_model) %>%
    as.data.frame %>%
    rownames_to_column (var = "Variable") %>%
    mutate (`%IncMSE` = `%IncMSE` / max (`%IncMSE`)) %>%
    mutate (type = "Random forest")

@@

```{r, fig.width = 10, fig.height = 12}
df_importance_xgb = xgboost::xgb.importance (model = xgboost_model) %>%
    mutate (Gain = Gain / max (Gain)) %>%
    mutate (type = "Gradient boosting")

@@

```{r, include = FALSE}
png (file = "figures/Figure_6.png", width = 1000, height = 800)
Figure_6
dev.off()
```

@@

```{r, include = FALSE}
png (file = "figures/Figure_8.png", width = 1200, height = 800)
Figure_8
dev.off()
```

@@

plot_shap_rf_2 = plot_shap_rf +
    annotate (geom = "label", label = "Random forest", size = 11, family = "Times",
    label.padding = unit(0.8, "lines"), fontface = "bold", x = 38.5, y = 1.5, fill = "#000080", color = "white") +
    xlim (c (- 18, 45)) +
    theme (legend.position = "none", 
          plot.margin = unit (c (0, 0, 1, 0), "cm"),
          axis.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks.x = element_blank())

plot_shap_xgboost_2 = plot_shap_xgboost +
    annotate (geom = "label", label = "Gradient boosting", size = 11, family = "Times",
    label.padding = unit(0.8, "lines"), fontface = "bold", x = 36.8, y = 1.5, fill = "#000080", color = "white") +
    xlim (c (- 18, 45)) + 
    theme (legend.position = "none", 
          plot.margin = unit (c (0, 0, 1, 0), "cm"),
          axis.title.x = element_text (margin = ggplot2::margin (t = 10, b = 20)))

png (file = "figures/Figure_5.png", width = 1000, height = 900)
do.call ("grid.arrange", 
         c (list(plot_shap_rf_2, 
                 plot_shap_xgboost_2, 
                 legend), 
            list(layout_matrix = as.matrix(c (1, 2, 3)),
                  heights = c (0.8, 1, 0.2))))
dev.off()

```

```{r}
tiff (file = "figures/Figure_5.tiff", width = 1000, height = 900)
do.call ("grid.arrange", 
         c (list(plot_shap_rf_2, 
                 plot_shap_xgboost_2, 
                 legend), 
            list(layout_matrix = as.matrix(c (1, 2, 3)),
                  heights = c (0.8, 1, 0.2))))
dev.off()
```

@@

```{r}
png (file = "figures/Figure_4.png", width = 1300, height = 800)
grid.arrange (plot_importance_rf, plot_importance_xgboost, nrow = 1)
dev.off()
```

@@

```{r, fig.height = 5, fig.width = 7}
Figure_7 = data_alfam2 %>%
    mutate (man.source = recode (man.source, "cat" = "Cattle", "pig" = "Pig")) %>%
    ggplot () +
        geom_boxplot (aes (x = man.source, y = tan.app)) +
        ylab ("TAN") +
        xlab ("Manure source") +
        theme (axis.text.x = element_text(margin = ggplot2::margin(t = 10))) +
        NULL

@@

```{r, include = FALSE}
png (file = "figures/Figure_7.png", width = 1200, height = 800)
Figure_7
dev.off()
```

@@

```{r, fig.height = 8, fig.width = 10}
Figure_9 = rbind (
    data %>% select (temp = Tem) %>% mutate (data = "Data from Xu et al (2024)"),
    data_alfam2 %>% select (temp = air.temp) %>% mutate (data = "Data used for the alfam2 model")
) %>%

@@

```{r, include = FALSE}
png (file = "figures/Figure_9.png", width = 1000, height = 600)
Figure_9
dev.off()
```

```{r}
rbind (
    data %>% select (temp = Tem) %>% mutate (data = "Data from Xu et al (2024)"),
    data_alfam2 %>% select (temp = air.temp) %>% mutate (data = "Data used for the alfam2 model")
) %>%
